\documentclass[11pt]{beamer}
\usetheme{Warsaw}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Brendan Benshoof}
\title{Survey of Parallel Convex Hull Algorithims}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\date{} 
%\subject{} 
\begin{document}
\setcounter{tocdepth}{3}
\begin{frame}
\titlepage
\end{frame}

\section{Overview}
\begin{frame}{Problem Overview}
\end{frame}


\begin{frame}{Division of Works}

Works examined fall roughly into 3 main approaches
\begin{itemize}
\item{ Divide and Conquer Methods}
\begin{itemize}
\item{``Efficient parallel solutions to some geometric problems.''}
\item{ ``Scalable 2d convex hull and triangulation algorithms for coarse grained multicomputers.''}
\item{``Efficient parallel convex hull algorithms.''}
\end{itemize}
\item{ Qhull derived methods}
\begin{itemize}
\item{``The quickhull algorithm for convex hulls.''}
\item{ ``Parallel implementation of 3D convex-hull algorithm.''}
\item{``Fast two dimensional convex hull on the GPU.''}
\item{``CudaHull: Fast parallel 3D convex hull on the GPU''}
\item{``Parallel algorithms for higher-dimensional convex hulls.''}
\end{itemize}
\item{ Sampling Based Methods}
\begin{itemize}
\item{``A randomized parallel 3D convex hull algorithm for coarse grained multicomputers.''}
\item{ ``Fast randomized parallel methods for planar convex hull construction.''}
\end{itemize}

\end{itemize}

\end{frame}




\section{Divide and Conquer}
\begin{frame}{Overview}
\end{frame}

\begin{frame}{Efficient parallel solutions to some geometric problems}
\end{frame}
\begin{frame}{Scalable 2d convex hull and triangulation algorithms for coarse grained multicomputers.}
\end{frame}
\begin{frame}{Efficient parallel convex hull algorithms.}
\end{frame}





\section{Qhull}

\begin{frame}{Overview}
\end{frame}

\begin{frame}{The quickhull algorithm for convex hulls.}
\end{frame}
\begin{frame}{Parallel implementation of 3D convex-hull algorithm.}
\end{frame}
\begin{frame}{Fast two dimensional convex hull on the GPU.}
\end{frame}
\begin{frame}{CudaHull: Fast parallel 3D convex hull on the GPU.}
\end{frame}
\begin{frame}{Parallel algorithms for higher-dimensional convex hulls.}
\end{frame}


\section{Sampling Methods}
\begin{frame}{Overview}
\end{frame}
\begin{frame}{A randomized parallel 3D convex hull algorithm for coarse grained multicomputers.}
\end{frame}
\begin{frame}{Fast randomized parallel methods for planar convex hull construction.}
\end{frame}


\end{document}